Application-Level Regression Testing Framework using Jenkins

### 2017-04-12 manuscript/manuscript.tex
Added reference, small addition in conclusion. Work in progress, won't build in latex.

\documentclass[10pt, conference, compsocconf]{IEEEtran}

@@

@@

\subsection{Special Projects}
The initial display tabs (i.e. Jenkins ''Views``) in our Jenkins instance are used to group tests that are run periodically in production. We add separate ''Views`` for special projects. For example we clone existing tests for evaluating a new software stack on our test login node (''h2ologin4`` view).  Our TDS (JYC) has a separate set of tests from our production system and is used as our Jenkins development mule. The sustained petascale performance benchmarks (SPP) are in their own tab because they run at scale and are only run on-demand by staff (i.e. not scheduled to run periodically by Jenkins}. Figure \ref{fig:tabs-display} illustrates our use of Jenkins views to organize our application tests.
\begin{figure}[H]
\centering
\includegraphics[width=0.5\textwidth]{tabs-display}
\caption{Jenkins views (tabs) in our instance.}
\label{fig:tabs-display}
\end{figure}

@@

>>>>

%\documentclass[10pt, conference, compsocconf]{IEEEtran}
\documentclass{sig-alternate-05-2015}

@@

\setcopyright{licensedusgovmixed}

@@

\subsection{Special Projects}
The initial display tabs (i.e. Jenkins ''Views``) in our Jenkins instance are used to group tests that are run periodically in production. We add separate ''Views`` for special projects. For example we clone existing tests for evaluating a new software stack on our test login node (''h2ologin4`` view).  Our TDS (JYC) has a separate set of tests from our production system and is used as our Jenkins development mule. The sustained petascale performance benchmarks (SPP) are in their own tab because they run at scale and are only run on-demand by staff (i.e. not scheduled to run periodically by Jenkins). Figure \ref{fig:tabs-display} illustrates our use of Jenkins views to organize our application tests.
\begin{figure}[H]
\centering
\includegraphics[width=0.5\textwidth]{tabs-display}
\caption{Jenkins views (tabs) in our instance.}
\label{fig:tabs-display}
\end{figure}

@@

Due to our initial successful deployment of Jenkins as regression testing framework on NCSA and NICS resources,  it is currently being deployed on other resources including the CADES (Compute and Data Environment for Science) resources at the Oak Ridge National Laboratory.
